Outdated and License-Violating Code on Stack Overflow

### 2017-02-26 cloneoverflow-latex/cloneoverflow.tex
Added medians of SO snippets and Qualitas (also updated the other numbers since I just found cloc option to not skip duplicated files).

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. 
% The archived dump has a size of 9 gigabytes. 
The data
dump is in XML format containing information of posts
(questions and answers) and 
% supporting data such as user accounts and timestamps of the posts.
we were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,346,267
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
% excluding comments and blank lines.

\textbf{Open source systems: }
We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus} 
for this study. It is a curated Java corpus that has been used in several
software engineering
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
projects in the corpus represent various domains of software systems
ranging from programming languages to
visualisation. We selected the 20130901r release
of the Qualitas corpus containing 112 Java open source projects. This
release contains projects with releases no later than 1st September
2013. We intentionally chose an old corpus from 2013 since we are interested in
online code clones in the direction from open source projects to Stack
Overflow. The 20130901r snapshot provides Java code that is more than
2 years older than the Stack Overflow snapshot, which is sufficiently
long for a number of code snippets to be copied onto Stack Overflow
and also to observe if clones become outdated. Out of 112 Qualitas
projects, there is one project, \textsf{jre}, that does not contain
Java source code due to its licensing limitation~\cite{QualitasCorpus}
and is removed from the study. This resulted in a total of 111
projects analysed in the study. As shown in \Cref{tab:datasets}, the
111 Qualitas project have 160,937 Java files containing 19,086,883
lines of
code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

\begin{table}
  \centering
  \caption{Stack Overflow and Qualitas datasets}
  \label{tab:datasets}
  %\small
  \begin{tabular}{lrr}
    \hline 
    Dataset & No. of files & SLOC \\
    \hline
    Stack Overflow & 144,064 & 2,346,267 \\ 
    %\hline 
    Qualitas &  160,937 & 19,086,883 \\ 
    \hline 
  \end{tabular} 
\end{table}

>>>>

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. 
% The archived dump has a size of 9 gigabytes. 
The data
dump is in XML format containing information of posts
(questions and answers) and 
% supporting data such as user accounts and timestamps of the posts.
we were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,332,940
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
Median of the snippet size is 10.
% excluding comments and blank lines.

\textbf{Open source systems: }
We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus} 
for this study. It is a curated Java corpus that has been used in several
software engineering
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
projects in the corpus represent various domains of software systems
ranging from programming languages to
visualisation. We selected the 20130901r release
of the Qualitas corpus containing 112 Java open source projects. This
release contains projects with releases no later than 1st September
2013. We intentionally chose an old corpus from 2013 since we are interested in
online code clones in the direction from open source projects to Stack
Overflow. The 20130901r snapshot provides Java code that is more than
2 years older than the Stack Overflow snapshot, which is sufficiently
long for a number of code snippets to be copied onto Stack Overflow
and also to observe if clones become outdated. Out of 112 Qualitas
projects, there is one project, \textsf{jre}, that does not contain
Java source code due to its licensing limitation~\cite{QualitasCorpus}
and is removed from the study. This resulted in a total of 111
projects analysed in the study. As shown in \Cref{tab:datasets}, the
111 Qualitas project have 166,709 Java files containing 19,614,083
lines of code. Median of the project size is 60,667 lines of code.

\begin{table}
  \centering
  \caption{Stack Overflow and Qualitas datasets}
  \label{tab:datasets}
  %\small
  \begin{tabular}{lrrr}
    \hline 
    Dataset & No. of files & SLOC & Median \\
    \hline
    Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
    %\hline 
    Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
    \hline 
  \end{tabular} 
\end{table}
